---
title: "Data Anaysis and Unsupervised Learning"
subtitle: "Introduction"
author: "Julien Chiquet"
institute: "UMR MIA Paris-Saclay, AgroParisTech, INRAE"
date: 05/25/2023
date-format: long
format: beamer
---


 <!-- ==================================================================== -->
\part{Introduction}
 <!-- ==================================================================== -->

```{r introduction, child='introduction.qmd'}
```

---
<!-- ==================================================================== -->
\part{Principal Component Analysis}
<!-- ==================================================================== -->

```{r intro_pca, child='intro_pca.qmd'}
```
```{r background_pca, child='background_algebra.qmd'}
```

 <!-- Geometrical point of View -->
 ```{r geometry, child='geometry_PCA.qmd'}
 ```
<!-- Principal axes by variance maximization -->
```{r fitting, child='fitting_PCA.qmd'}
```
 <!-- Representation and interpretation -->
```{r representation, child='representation.qmd'}
```
 <!-- Complements, reconstructIon -->
```{r complements, child='complements_pca.qmd'}
```

<!-- ==================================================================== -->
\part{probabilistic Principal Component Analysis}
<!-- ==================================================================== -->

<!-- Gaussian model -->
<!-- model selection -->
<!-- Estimation with ML and EM -->



<!-- Poisson PCA -->
<!-- estimation with variaitonal EM -->

<!-- ==================================================================== -->
\part{(Variational) Auto-Encoder}
<!-- ==================================================================== -->


\subsection{PCA as a matrix factorization}
<<Reconstruction error, child='reconstruction_error_viewpoint.Rnw'>>=
@

\subsection{Kernel-PCA}
<<Kernel PCA, child='kernelPCA.Rnw'>>=
@

\subsection{Non-negative matrix factorization}
<<NMF, child='NMF.Rnw'>>=
@

\subsection{Other directions}
<<others reconstruction, child='others_reconstruction.Rnw'>>=
@

%% ==========================================================================
\section{Motivated by relation preservation}
%% ==========================================================================

<<Relation preservation, child='relation_preservation_viewpoint.Rnw'>>=
@

\subsection{Multidimensional Scaling}
<<MDS, child='MDS.Rnw'>>=
@

\subsection{Stochastic Neighborhood Embedding}
<<tSNE, child='tSNE.Rnw'>>=
@

\subsection{Other methods}
<<others relation, child='others_relation.Rnw'>>=
@


